### 2016-10-19 R/ITHIM.Rmd
Updated figures 2 and 3 for methods paper

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(45, 120, length.out = 5)
muNonTravelVec <- c(1, 10, 50, 100, 150, 200)
DTotal <- data.frame()

@@

```{r displayMeans, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
D <- rbind(getWalkTime(ITHIM.default),getWalkSpeed(ITHIM.default),getCycleTime(ITHIM.default),getNonTravelMETs(ITHIM.default))
D <- within(D, sex <- factor(sex, levels = c("F","M")))

p <- ggplot(D, aes(x = ageClass, y = mu, fill = sex)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + scale_x_discrete(name="", labels = c("0-4","5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="Travel Time per Week (minutes)") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 10)) + facet_grid( type ~ ., scales = "free_y")
```

```{r displayGBD, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
D <- melt(ITHIM.default$parameters$GBD)
names(D) <- c("disease","sex","ageClass","type","burden", "sex2", "disease2")
D <- within(D, sex <- factor(sex, levels = c("F","M")))

p <- ggplot(subset(D,disease %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes")), aes(x = ageClass, y = burden, fill = sex)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + scale_x_discrete(name="", labels = c("0-4","5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 10)) + facet_grid( type ~ disease, scales = "free_y")
```

>>>>

DALYs <- c(); DALYs.quints <- c();
atVec <- seq(45, 120, length.out = 5)
muNonTravelVec <- c(1, 5, 10)
DTotal <- data.frame()

@@

```{r displayMeans, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = phi, warning = FALSE, message = FALSE, echo = FALSE}

ITHIM.national <- updateITHIM(ITHIM.national, "muNonTravel", 5)

D <- rbind(getWalkTime(ITHIM.national),getWalkSpeed(ITHIM.national),getCycleTime(ITHIM.national),getNonTravelMETs(ITHIM.national))
D <- within(D, sex <- factor(sex, levels = c("F","M")))

p <- ggplot(D, aes(x = ageClass, y = mu, fill = sex)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + scale_x_discrete(name="", labels = c("0-4","5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 8)) + facet_grid( type ~ ., scales = "free")
```

## Figure 3

```{r displayGBD, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = FALSE}
D <- melt(ITHIM.national$parameters$GBD)
names(D) <- c("disease","sex","ageClass","type","burden", "sex2", "disease2")
D <- within(D, sex <- factor(sex, levels = c("F","M")))

p <- ggplot(subset(D, disease %in% c("BreastCancer","ColonCancer","Dementia","Depression","Diabetes")), aes(x = ageClass, y = burden/1e3, fill = sex)) + geom_bar(stat= "identity", position = "dodge")
p + theme_bw() + scale_x_discrete(name="", labels = c("0-4","5-14","15-29","30-44","45-59","60-69","70-79","80+")) + scale_y_continuous(name="Nationwide Burden (thousands)") + theme(axis.text.x  = element_text(angle = 90, vjust = 0.5, size = 10)) + facet_grid( type ~ disease, scales = "free_y")
```
